Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-16 latex/article.tex

A {\em cell} $(k,x,y,z)$ is a region of the space of size $2^k \times
2^k \times 2^k$, characterized by its integer coordinates $x,y,z$,
with $0 \le x < 2^k$, $0 \le y < 2^k$, $0 \le z < 2^k$. Cells forms an
octree decomposition of a cubic space. We use functions Up, Down and
Next to navigate between cells.

\begin{algorithm}
\KwIn{Integers $p,q,r$ \tcp*{the moment orders, with $0 \le p+q+r \le 2$}}
\KwIn{Integer $k$ \tcp*{$(2^k)^3$ is the size of the digital shape image}}
\KwIn{Mipmap $V$ \tcp*{array of $k+1$ images of sizes $(2^k)^3,  (2^{k-1})^3, \ldots,  1^3$}}
\KwIn{Integers $x_0,y_0,z_0$, Real $r$ \tcp*{Ball radius $r$ and center $(x_0,y_0,z_0)$}}
\KwOut{Real $m$ \tcp*{estimation of the $p,q,r$-moment of $X \cap B_r(x_0,y_0,z_0)$}}
\KwData{Cell $c :=  (k,0,0,0)$ \tcp*{Starts from biggest cell}}
\KwData{Integer $n := 2^k$ \tcp*{Size of each cell}}
\KwData{Real $d,\delta,l$ \tcp*{variables for intermediate computations}}
\Begin{
    m := 0 \;
    \Repeat{$c[0] = k$}{
      \tcp{Distance between cell and ball centers}
      $d := \frac{1}{2}\| 2^k(2c[1]+1,2c[2]+1,2c[3]+1) - (2x_0+1,2y_0+1,2z_0+1) \|_2$\;
      $\delta := \frac{\sqrt{3}}{2}2^{c[0]}$ \tcp*{half-length of cell diagonal}
      \If(\tcp*[f]{Is it a smallest cell ?}){$c[0] = 0$}{
        \If(\tcp*[f]{Is cell inside ball ?}){$d^2 \le r^2$}{
          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$
        }
        $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
      } \Else{
        $l := \max(r-\delta,0)$\;
        \If(\tcp*[f]{Is cell completely inside ball ?}){$d^2 < l^2$}{
          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$
          $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
        }\ElseIf(\tcp*[f]{Is cell outside ball ?}){$d^2 > (r+\delta)^2$}{
          $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
        }\lElse(\tcp*[f]{Go to a finer cell}){$c := \textsc{Down}(c)$}
      }
    }
    \Return{m}\;
  }
  \caption{Derecursified hierarchical algorithm for computing the
    $p,q,r$-moment of set $X \cap B_r(x_0,y_0,z_0)$, given a mipmap
    $V$ that represents the volume of a shape $X$ in each cell, and
    ball parameters $x_0,y_0,z_0,r$.}
\end{algorithm}

>>>>

A {\em cell} is a tuple $(k,x,y,z)$, which represents a region of the space of size $2^k \times
2^k \times 2^k$, characterized by its integer coordinates $x,y,z$,
with $0 \le x < 2^k$, $0 \le y < 2^k$, $0 \le z < 2^k$. Cells forms an
octree decomposition of a cubic space. We use functions Up, Down and
Next to navigate between cells.

\begin{algorithm}
\KwIn{Integers $p,q,r$ \tcp*{the moment orders, with $0 \le p+q+r \le 2$}}
\KwIn{Integer $k$ \tcp*{$(2^k)^3$ is the size of the digital shape image}}
\KwIn{Mipmap $V$ \tcp*{array of $k+1$ images of sizes $(2^k)^3,  (2^{k-1})^3, \ldots,  1^3$}}
\KwIn{Integers $x_0,y_0,z_0$, Real $r$ \tcp*{Ball radius $r$ and center $(x_0,y_0,z_0)$}}
\KwOut{Real $m$ \tcp*{estimation of the $p,q,r$-moment of $X \cap B_r(x_0,y_0,z_0)$}}
\KwData{Cell $c :=  (k,0,0,0)$ \tcp*{Starts from biggest cell}}
\KwData{Integer $n := 2^k$ \tcp*{Size of each cell}}
\KwData{Real $d,\delta,l$ \tcp*{variables for intermediate computations}}
\Begin{
    m := 0 \;
    \Repeat{$c[0] = k$}{
      \tcp{Distance between cell and ball centers}
      $d := \frac{1}{2}\| 2^k(2c[1]+1,2c[2]+1,2c[3]+1) - (2x_0+1,2y_0+1,2z_0+1) \|_2$\;
      $\delta := \frac{\sqrt{3}}{2}2^{c[0]}$ \tcp*{half-length of cell diagonal}
      \If(\tcp*[f]{Is it a unit cell ?}){$c[0] = 0$}{
        \If(\tcp*[f]{Is cell center inside ball ?}){$d^2 \le r^2$}{
          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$ \;
        }
        $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
      } \Else{
        $l := \max(r-\delta,0)$\;
        \If(\tcp*[f]{Is cell completely inside ball ?}){$d^2 < l^2$}{
          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$\;
          $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
        }\ElseIf(\tcp*[f]{Is cell outside ball ?}){$d^2 > (r+\delta)^2$}{
          $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
        }\lElse(\tcp*[f]{Go to a finer cell}){$c := \textsc{Down}(c)$}
      }
    }
    \Return{m}\;
  }
  \caption{Derecursified hierarchical algorithm for computing the
    $p,q,r$-moment of set $X \cap B_r(x_0,y_0,z_0)$, given a mipmap
    $V$ that represents the volume of a shape $X$ in each cell, and
    ball parameters $x_0,y_0,z_0,r$.}
\end{algorithm}
